%% document class
\documentclass[14pt, a4paper]{extreport}

%% packages 
\input{settings/packages}

%% page settings 
\input{settings/page}

%% own commands 
\newcommand{\tbi}[1]{\textbf{\textit{#1}}}
\input{settings/macros}

%--------------------------------------------------------
\begin{document}

\input{content/title_page}

\pagestyle{plain}

\begin{abstract}
NeuraLearn Academy is an innovative educational platform leveraging generative AI and Large Language Models (LLMs) to enhance online learning experiences.This platform introduces new workflows utilizing AI technologies, benefiting both instructors and students. Despite the rapid growth of online education, traditional platforms often struggle with issues such as limited interactivity, lack of personal engagement, and reliance on digital assessments. The primary objective of our proposed Model NeuraLearn Academy is to revolutionize online learning by integrating generative AI and Large Language Models (LLMs). For instructors, the platform provides deep learning systems to facilitate the generation of insightful questions and summaries, enhancing teaching effectiveness. Meanwhile, students benefit from the Retrieval-Augmented Generation (RAG) architecture, enabling interactive educational chats that foster deeper understanding and engagement with course material.our proposed Model have demonstrated exceptional performance in question generation and summarization tasks. Our question generation model achieved ROUGE scores of 40\% in ROUGE-1, 20\% in ROUGE-2, and 39\% in ROUGE-L. Similarly, our summarization model excelled on the BookSum benchmark with scores of 33\% in ROUGE-1, 5.2\% in ROUGE-2, 23\% in ROUGE-L, and 29.977\% in ROUGE-LSUM. These results affirm the effectiveness of our approach in enhancing educational interactions and content comprehension in online learning environments.

\end{abstract}
    
\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
    We would like to take this opportunity to express our sincere
    appreciation and best wishes to our devoted supervisor, Dr. Jehad,
    for her great leadership and ongoing motivation during the completion of
    this project. The assistance, and guidance she occasionally provided will
    help us get far along in the life's journey we are about to take.

    We also take this occasion to thank Faculty of Computers and
    Artificial Intelligence Council for their support and work in getting us all
    the resources we need.

    We would especially like to thank the FCAI members for the useful
    information they gave in their respective domains.
    Finally, we express our gratitude to Almighty, our parents, and
    everyone who has provided assistance, encouragement, and support.
\end{abstract}

    

\tableofcontents 
\listoffigures
\listoftables


\include{chapters/chapter1}
\include{chapters/chapter2}
\include{chapters/chapter3}
\include{chapters/chapter4}
\include{chapters/chapter5}

\renewcommand{\bibname}{References}
\bibliographystyle{plain}
\bibliography{bib}
\end{document}
